---
title: "Replication for 'Ticket Splitting in a Nationalized Era'"
author: "Shiro Kuriwaki"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

This repository is a replication archive for the manuscript, "Ticket Splitting in a Nationalized Era". 

Both a Dataverse version and a [Github version](https://github.com/kuriwaki/ticketsplit-JOP) are available. 


## How to Replicate 

I strongly recommend downloading this entire repository and opening it as __a [RStudio](https://posit.co/download/rstudio-desktop) Project__.
This will activate the package manager **renv** easily. Specifically:

1. In RStudio, create a new Rstudio project. 
    a. If you downloaded the packet from Dataverse, you can open the `ticketsplit-JOP.Rproj` file. 
    b. If you are starting from Github, start from your local RStudio and create a [new project](https://support.posit.co/hc/en-us/articles/200526207-Using-RStudio-Projects) with the option of `Create from Version Control` > `Git`, and this this URL <https://github.com/kuriwaki/ticketsplit-JOP>.
2. A new Project should open. Run `renv::restore()` to download the necessary packages with their versions in one step.  
3. Then, inside the Rstudio and renv environment, replicators can run the master script `00_replicate-ALL.R` or run each R script. 

See the "package and dependencies" section for more on replication environment.


## Project Structure

This repository has the following scripts. The name of the file indicates the figure / table that it reproduces.
For example, `02_fig-02-B5_topline.R` indicates that it creates Figure 2 and Figure B5.

```{r, echo=FALSE}
fs::dir_ls(".", regexp = ".R$")
```
All scripts default to the project directory (e.g., "ticketsplit-JOP", or where the `.Rproj` file is located) as its working directory.

## Datasets

The data in this archive include standard `csv` files, Stata `dta` files (which should be read in with `.dta`) and parquet files (`.parquet`). 
The parquet files are compact storage formats for large datasets and allows the models to be run quickly. It can be loaded with the `arrow` package using the `open_dataset()` function. For a reference, see <https://r4ds.hadley.nz/arrow>. 

## Packages and Dependencies (renv)

This repository uses R. It uses the [renv package](https://rstudio.github.io/renv) to manage package versions, so that there are no internal inconsistencies on your computer 
The `renv.lock` file encodes all the  necessary dependencies. 
Opening the project in Rstudio Projects will automatically register the lockfile (from the `.Rprofile`), and Rstudio Projects will ask if you want to install missing packages. 
You can install the missing packages using `renv::restore()`. 
See <https://rstudio.github.io/renv/articles/renv.html> for more help on how to start this. 

For reference, here are the package dependencies across all scripts, from most used to least (renv will instlal these for you).

```{r, echo=FALSE, message=FALSE}
renv::dependencies() |> 
  dplyr::as_tibble() |> 
  dplyr::count(Package, sort = TRUE) |> 
  dplyr::pull(Package) |> 
  dput()
```


All packages are on CRAN except `ticketsplitJOPpkg`, which is a bundle of extra functions specific to this repository. 
It is available at <https://github.com/kuriwaki/ticketsplitJOPpkg>. `renv` will install this for you, but it can also be manually installed with 

```{r, eval=FALSE}
remotes::install_github("kuriwaki/ticketsplitJOPpkg")
```

